Template Master's Thesis

### 2023-08-22 paper.tex
Clean paper

\vspace{2em}

@@

\begin{table}[h!]
\scriptsize
  \centering
  \begin{tabular}{lrrr}
    \hline
	\textbf{ENS domain name} & \textbf{Diff2Vec} & \textbf{Role2Vec} & \textbf{DeepWalk} \\
	\hline
	anisofim.eth & 2.5 & 6.2 & 2.7 \\
	arisalzberg.eth & 577.3 & 33.3 & 58.8 \\
	atearnz.eth & 2.8 & 2.5 & 3.3 \\
	awedjob.eth & 106.8 & 71.1 & 20.1 \\
	captvicky.eth & - & - & - \\
	disruptor.eth & 11.1 & 3.0 & 1.4 \\
	dragonkiller.eth & 30.7 & 1.0 & 1.0 \\
	eibriel.eth & 44.3 & 91.2 & 545.4 \\
	epdrabbit.eth & 16.3 & 10.4 & 4.1 \\
	erikarand.eth & 1.0 & 1.0 & 1.0 \\
	hyperspek.eth & 129.1 & 10.0 & 605.4 \\
	jamesmillerblog.eth & - & - & - \\
	jasonhsu.eth & 1.0 & 1.0 & 1.8 \\
	joeyz.eth & 1.9 & 1.0 & 1.0 \\
	keastie.eth & 10.4 & 1.0 & 18.2 \\
	linkg.eth & 4.0 & 1.0 & 10.3 \\
	lulox.eth & 4.2 & 1.5 & 27.2 \\
	maruudn.eth & 5.7 & 5.6 & 108.5 \\
	maryana.eth & 52.3 & 373.8 & 9.0 \\
	meanboss.eth & 9.0 & 9.0 & 51.8 \\
	metatiger.dcl.eth & 474.2 & 86.7 & 2.4 \\
	mgdivingnz.eth & 1.7 & 5.0 & 1.0 \\
	mrcryp.eth & 2.7 & 1.0 & 2.3 \\
	nicebhaiya.eth & 1.3 & 3.4 & 2.4 \\
	niceguy.eth & 1.0 & 1.0 & 2.2 \\
	ornellaweb3.eth & 3.7 & 2.0 & 284.0 \\
	pinkboots.eth & 16.9 & 14.4 & 2.2 \\
	remx.eth & 3.6 & 2.6 & 1.7 \\
	rileybeans.eth & 1.5 & 2.0 & 1.6 \\
	robertjames.eth & 2.7 & 1.0 & 1.1 \\
	rsantos.eth & 2.0 & 13.6 & 101.2 \\
	sannin.eth & 64.8 & 1.1 & 1.6 \\
	smileface.eth & 3.0 & 19.3 & 1.7 \\
	theartcollection.eth & 11.0 & 5.6 & 3.4 \\
	turkii13.eth & 52.1 & 68.9 & 47.3 \\
	tweetious.eth & 10.3 & 4.0 & 227.0 \\
    \hline
    Mean & 46.038 & 28.073 & 62.084 \\
    Median & 4.2 & 3.4 & 3.3 \\
    Standard deviation & 120.504 & 68.814 &  139.932\\
    Within 5 nearest neighbors & 17 (0.5) & 19 (0.56) & 20 (0.59) \\
    Within 10 nearest neighbors & 19 (0.56) & 24 (0.71) & 21 (0.62)\\
    \hline
  \end{tabular}
  \caption{Average Rank of ENS Domain Names for Different Embedding Methods, Addresses outside of largest connected component have a NaN value}
  \label{tbl:ENS_Domain_Ranks}
\end{table}

@@

\begin{table}[h!]
\small
  \centering
  \begin{tabular}{lrrrrrrr}
    \hline
	\textbf{Threshold} & \textbf{0.5} & \textbf{0.55} &\textbf{0.6} & \textbf{0.65} & \textbf{0.7} & \textbf{0.75} & \textbf{0.8} \\
	\hline
Total clusters 			& 29,502 & 26,762 & 23,608 & 21,229 & 18,592 & 16,361 & 14,793 \\
Size of largest cluster & 499 & 	512 & 516 & 	524 & 532 & 535 & 544\\
Clusters of size 50+ 	& 2 & 2 & 3 & 7 & 9  & 13 & 14\\
    \hline
  \end{tabular}
  \caption{Clustering results for different threshold values}
  \label{tbl:cluster_table}
\end{table}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.65\textwidth]{../figures/land_network.png}
	\caption{LAND token network}
	\label{fig:LAND_network}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/network_visualization_0xe2e.png}
	\caption{Token Transfer Graph for \texttt{0xE2e2F$\dots$faCa8}}
	\label{fig:cluster}
\end{figure}

%\textbf{LAND transfers}\\
The \textit{LAND transfer} heuristic is targeted at users revealing address clusters by sending high-value assets to other addresses. In this specific case, we use the information that all addresses are related to Decentraland and therefore analyze LAND transfers. However, the approach could be applied (more generally) to other NFT collections or large asset transfers in general. \newline
The main assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk across multiple accounts. As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets increased and their knowledge grew, they switched to a more secure hardware wallet. We detect 161 entities with 413 addresses applying this approach. One cluster with 70 address is very likely a not a single entity. It includes an address that participated in the intial LAND auction and subsequently distributed LAND. This may have happened through off-chain compensation. The advantage of this method is that it is relatively easy to visualise and understand. The disadvantage is that it demands a specific on-chain behaviour and is only scalable with significant effort. Additionally, many events that occur off-chain are not detectable in the data, resulting in an increased occurrence of false positives. 
%740 transfers, 413 addressen und 161 or 160 entities with 342 addresses. -The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address

@@

%% Table
\begin{table}[h!]
  \centering
  \tiny
  \begin{tabular}{ll p{4cm} l}
    \hline
    \textbf{Collection} & \textbf{Fields} & \textbf{Description} & \textbf{Example} \\ \hline
    Transactions & \texttt{\_id} & Unique identifier & 64b3c65ed2daf924bfdce72b
 \\
    (16.1M rows) & \texttt{hash} & Transaction hash & 0x8d9490e9f0992e68490cfcb126e76290eca3bf668a... \\
     & \texttt{timeStamp} & Timestamp in seconds from the UNIX epoch &  1657777314\\
     & \texttt{gasUsed} & Amount of gas used by the transaction &  144176  \\
     & \texttt{gasPrice} & The price of gas the originator is willing to pay &  12449848873 \\
     & \texttt{nonce} &   &   \\
     & \texttt{from} & Address initiating the transaction &   \\
     & \texttt{to} & The destination address (either native asset transfer or function call) &  \\
     & \texttt{value} & The amount of Ether/Matic to send to the destination & 500 \\
     & \texttt{input} & Calldata & 0x095ea7b30000000000000000000000001111111254fb6c44bac0bed2854e76f90643097dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff \\
     & \texttt{functionName} & added by Etherscan & approve(address spender, uint256 rawAmount) \\
     & \texttt{chainName} & Chain indicator & Ethereum or Polygon \\
    \hline
    Transfers & \texttt{\_id} & see above & see above\\
    (36.4M rows) & \texttt{hash} & see above & see above \\
     & \texttt{timeStamp} & see above & see above\\
     & \texttt{gasUsed} & see above &  see above\\
     & \texttt{gasPrice} & see above & see above \\
     & \texttt{nonce} &  see above & see above \\
     & \texttt{from} &  Sender address & see above \\
     & \texttt{to} &  Recipient address & see above \\
     & \texttt{value} & Amount of tokens transferred in Wei, only for fungible or semi-fungible tokens & 10000000000000000 or NaN (ERC-721) \\
     & \texttt{tokenID} &  Identifier of the NFT or semi-fungible token &  or NaN (ERC20) \\
     & \texttt{contractAddress} & The token contract address &  0xc02aaa39b223fe8d0a0e5c4f27ead9083c756cc2 \\
     & \texttt{tokenName} & The specified token name &  Wrapped Ether\\
     & \texttt{tokenType} & Token standard indicator &  20 or 721 or 1155\\
     & \texttt{chainName} & see above &  see above \\
     & \texttt{isSet} & Indicator if from or to address are from address set &  from or to \\
     & \texttt{userAddress} & Address of interested user & 0x000000085d9a759bb5c3d459d638739c0f48deb0\\
    \hline
  \end{tabular}
  \caption{Database/data set Description}
  \label{tbl:database_schema}
\end{table}

>>>>

@@

\begin{table}[h!]
\scriptsize
  \centering
  \begin{tabular}{lrrr}
    \hline
	\textbf{ENS domain name} & \textbf{Diff2Vec} & \textbf{Role2Vec} & \textbf{DeepWalk} \\
	\hline
	anisofim.eth & 2.5 & 6.2 & 2.7 \\
	arisalzberg.eth & 577.3 & 33.3 & 58.8 \\
	atearnz.eth & 2.8 & 2.5 & 3.3 \\
	awedjob.eth & 106.8 & 71.1 & 20.1 \\
	captvicky.eth & - & - & - \\
	disruptor.eth & 11.1 & 3.0 & 1.4 \\
	dragonkiller.eth & 30.7 & 1.0 & 1.0 \\
	eibriel.eth & 44.3 & 91.2 & 545.4 \\
	epdrabbit.eth & 16.3 & 10.4 & 4.1 \\
	erikarand.eth & 1.0 & 1.0 & 1.0 \\
	hyperspek.eth & 129.1 & 10.0 & 605.4 \\
	jamesmillerblog.eth & - & - & - \\
	jasonhsu.eth & 1.0 & 1.0 & 1.8 \\
	joeyz.eth & 1.9 & 1.0 & 1.0 \\
	keastie.eth & 10.4 & 1.0 & 18.2 \\
	linkg.eth & 4.0 & 1.0 & 10.3 \\
	lulox.eth & 4.2 & 1.5 & 27.2 \\
	maruudn.eth & 5.7 & 5.6 & 108.5 \\
	maryana.eth & 52.3 & 373.8 & 9.0 \\
	meanboss.eth & 9.0 & 9.0 & 51.8 \\
	metatiger.dcl.eth & 474.2 & 86.7 & 2.4 \\
	mgdivingnz.eth & 1.7 & 5.0 & 1.0 \\
	mrcryp.eth & 2.7 & 1.0 & 2.3 \\
	nicebhaiya.eth & 1.3 & 3.4 & 2.4 \\
	niceguy.eth & 1.0 & 1.0 & 2.2 \\
	ornellaweb3.eth & 3.7 & 2.0 & 284.0 \\
	pinkboots.eth & 16.9 & 14.4 & 2.2 \\
	remx.eth & 3.6 & 2.6 & 1.7 \\
	rileybeans.eth & 1.5 & 2.0 & 1.6 \\
	robertjames.eth & 2.7 & 1.0 & 1.1 \\
	rsantos.eth & 2.0 & 13.6 & 101.2 \\
	sannin.eth & 64.8 & 1.1 & 1.6 \\
	smileface.eth & 3.0 & 19.3 & 1.7 \\
	theartcollection.eth & 11.0 & 5.6 & 3.4 \\
	turkii13.eth & 52.1 & 68.9 & 47.3 \\
	tweetious.eth & 10.3 & 4.0 & 227.0 \\
    \hline
    Mean & 46.038 & 28.073 & 62.084 \\
    Median & 4.2 & 3.4 & 3.3 \\
    Standard deviation & 120.504 & 68.814 &  139.932\\
    Within 5 nearest neighbors & 17 (0.5) & 19 (0.56) & 20 (0.59) \\
    Within 10 nearest neighbors & 19 (0.56) & 24 (0.71) & 21 (0.62)\\
    \hline
  \end{tabular}
  \caption{Average Rank of ENS Domain Names for Different Embedding Methods}
  \label{tbl:ENS_Domain_Ranks}
\end{table}

@@

\begin{table}[h!]
\scriptsize
  \centering
  \begin{tabular}{lrrrrrrr}
    \hline
	\textbf{Threshold} & \textbf{0.5} & \textbf{0.55} &\textbf{0.6} & \textbf{0.65} & \textbf{0.7} & \textbf{0.75} & \textbf{0.8} \\
	\hline
Total clusters 			& 29,502 & 26,762 & 23,608 & 21,229 & 18,592 & 16,361 & 14,793 \\
Size of largest cluster & 499 & 	512 & 516 & 	524 & 532 & 535 & 544\\
Clusters of size 50+ 	& 2 & 2 & 3 & 7 & 9  & 13 & 14\\
    \hline
  \end{tabular}
  \caption{Clustering results for different threshold values}
  \label{tbl:cluster_table}
\end{table}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{../figures/land_network.png}
	\caption{LAND token network}
	\label{fig:LAND_network}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.65\textwidth]{../figures/network_visualization_0xe2e.png}
	\caption{Token Transfer Graph for \texttt{0xE2e2F$\dots$faCa8}}
	\label{fig:cluster}
\end{figure}

The \textit{LAND transfer} heuristic is targeted at users revealing address clusters by sending high-value assets to other addresses. In this specific case, we use the information that all addresses are related to Decentraland and therefore analyze LAND transfers. However, the approach could be applied (more generally) to other NFT collections or large asset transfers in general. \newline
The main assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk across multiple accounts. As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets increased and their knowledge grew, they switched to a more secure hardware wallet. We detect 161 entities with 413 addresses applying this approach. One cluster with 70 address is very likely a not a single entity. It includes an address that participated in the intial LAND auction and subsequently distributed LAND. This may have happened through off-chain compensation. The advantage of this method is that it is relatively easy to visualise and understand. The disadvantage is that it demands a specific on-chain behaviour and is only scalable with significant effort. Additionally, many events that occur off-chain are not detectable in the data, resulting in an increased occurrence of false positives.

@@

%% Table
\begin{table}[h!]
  \centering
  \tiny
  \begin{tabular}{ll p{4cm} l}
    \hline
    \textbf{Collection} & \textbf{Fields} & \textbf{Description} & \textbf{Example} \\ \hline
    Transactions & \texttt{\_id} & Unique identifier & 64b3c65ed2daf924bfdce72b
 \\
    (16.1M rows) & \texttt{hash} & Transaction hash & 0x8d9490e9f0992e68490cfcb126e76290eca3bf668a... \\
     & \texttt{timeStamp} & Timestamp in seconds from the UNIX epoch &  1657777314\\
     & \texttt{gasUsed} & Amount of gas used by the transaction &  144176  \\
     & \texttt{gasPrice} & The price of gas the originator is willing to pay &  12449848873 \\
     & \texttt{nonce} &   &   \\
     & \texttt{from} & Address initiating the transaction &   \\
     & \texttt{to} & The destination address (either native asset transfer or function call) &  \\
     & \texttt{value} & The amount of Ether/Matic to send to the destination & 500 \\
     & \texttt{input} & Calldata & 0x095ea7b30000000000000000000000001111111254fb6c44bac0bed2854e76f90643097dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff \\
     & \texttt{functionName} & added by Etherscan & approve(address spender, uint256 rawAmount) \\
     & \texttt{chainName} & Chain indicator & Ethereum or Polygon \\
    \hline
    Transfers & \texttt{\_id} & see above & see above\\
    (36.4M rows) & \texttt{hash} & see above & see above \\
     & \texttt{timeStamp} & see above & see above\\
     & \texttt{gasUsed} & see above &  see above\\
     & \texttt{gasPrice} & see above & see above \\
     & \texttt{nonce} &  see above & see above \\
     & \texttt{from} &  Sender address & see above \\
     & \texttt{to} &  Recipient address & see above \\
     & \texttt{value} & Amount of tokens transferred in Wei, only for fungible or semi-fungible tokens & 10000000000000000 or NaN (ERC-721) \\
     & \texttt{tokenID} &  Identifier of the NFT or semi-fungible token &  or NaN (ERC20) \\
     & \texttt{contractAddress} & The token contract address &  0xc02aaa39b223fe8d0a0e5c4f27ead9083c756cc2 \\
     & \texttt{tokenName} & The specified token name &  Wrapped Ether\\
     & \texttt{tokenType} & Token standard indicator &  20 or 721 or 1155\\
     & \texttt{chainName} & see above &  see above \\
     & \texttt{isSet} & Indicator if from or to address are from address set &  from or to \\
     & \texttt{userAddress} & Address of interested user & 0x000000085d9a759bb5c3d459d638739c0f48deb0\\
    \hline
  \end{tabular}
  \caption{Database/data set Description}
\end{table}
